\section{Userstudy}

Our userstudy took place on Demo Day what allowed us to get a more or less diverse group of 12 test users, that were willing to take some of their time to fill in our questionnaire. \\
The majority was very familiar with AR/VR which is most likely due to us handing out the questionnaire during Demo Day, the most relevant event for games engineering students. \\
On a scale from 1 (bad) to 5 (good), previous knowledge about Celts was self-rated at ~1.92. After playing the game the self-rating on how much the test users learned about the Celtic culture was at 2.5. The test group was able to score 3.3 out of 6 possible points in the drawing quiz part, where they had to recognize 3 runes and write their meaning/name and 3 different rune names, where they had to draw the corresponding rune. \\
Overall, most of the testers liked the general tower defense concept with a score of 3.9 and liked our game with a score of 4.1. So the Celtic aspect increased the fun the testers had while playing the game. \\

\subsection{Suggestions for improvement}

The most frequent suggestion was, to reduce the amount of unlocked runes for every level in the campaign mode. For Demo Day we did not create a fully fleshed out campaign. We tried to keep the campaign relatively short to make it playable in a shorter amount of time, to make the game not as time consuming as it would be in the final version. \\
Furthermore, the marker-tracking performance was an issue for some testers despite our efforts to make it as stable as possible. Possible ways of improving AR further would be using a better device (computing power and better camera) and/or using advanced AR-libraries (ARCore/ARKit).
